Sparse Function-space Representation \\ of Neural Networks

### 2023-05-11 paper/main.tex
changed weights macro name

% Parameters
% \newcommand{\transitionParams}{\ensuremath{\bm\phi}}
\newcommand{\transitionParams}{\ensuremath{\mathbf{w}}}
\newcommand{\valueFnParams}{\ensuremath{\psi}}
\newcommand{\policyParams}{\ensuremath{\theta}}

% Networks
\newcommand{\transitionFnWithParams}{\ensuremath{\transitionFn_{\transitionParams}}}
\newcommand{\valueFn}{\ensuremath{\mathbf{Q}}}
\newcommand{\stateValueFn}{\ensuremath{\mathbf{V}}}
% \newcommand{\valueFn}{\ensuremath{\mathbf{Q}_{\valueFnParams}}}
\newcommand{\policy}{\ensuremath{\pi}}
\newcommand{\pPolicy}{\ensuremath{\pi_{\policyParams}}}

@@

\textbf{Neural Network} In supervised learning, given a data set $\dataset = \{(\mathbf{x}_{i} , \mathbf{y}_{i})\}_{i=1}^{n}$, with $\mathbf{x}_i \in \inputDomain$ and $\mathbf{y}_i \in \outputDomain$, the weights $\transitionParams \in \R^{P}$ of a neural network
, $f_\mathbf{w} : \inputDomain \mapsto \outputDomain$, 
are usually trained to minimize the (regularized) empirical risk,
\begin{align} \label{eq-empirical-risk}
  \transitionParams^{*} = 
  \argmin_{\transitionParams} \mathcal{L}(\dataset,\transitionParams) =
  \argmin_{\transitionParams} \sum_{i=1}^{n} \ell(f_\transitionParams(\mathbf{x}_{i}), \mathbf{y}_i) + \delta \mathcal{R}(\transitionParams).
\end{align}
If $\ell(f_\transitionParams(\mathbf{x}_{i}), \mathbf{y}_i) = -\log(p(\mathbf{y} \mid f_\transitionParams(\mathbf{x}_{i}))$ and $\mathcal{R}(\transitionParams) = \|\transitionParams\|^{2}_2$ then we can view \cref{eq-empirical-risk} as the MAP solution to a Bayesian objective, where $p(\vw) = \Norm(\vzeros, \delta^{-1} \MI)$.

@@

Given this interpretation, we can represent the weight space prior from \cref{eq-log-prior}, in
function space, by linearising the BNN around $\transitionParams^{*}$ and interpretting it as a GP.
The GP prior is then given by,
\begin{align} \label{eq-laplace-approx-function-space}
  % \transitionFn_{\transitionParams_{i}}(\cdot) \sim \mathcal{N} \left( \mu_{\transitionParams_{i}^{*}}(\cdot), K_{\transitionParams_{i}^{*}}(\cdot, \cdot') \right) \qquad
  g(\vx_i) \sim \mathcal{N} \left( \mu(\vx_i), k(\vx_i, \vx_i) \right) 
  % \mu_{\transitionParams_{i}^{*}}(\cdot)
  \mu(\cdot)
  = 0 \quad
  % = f(\cdot ;\transitionParams^{*}) \quad
  % K_{\transitionParams_{i}^{*}}(\cdot, \cdot')
  k(\mathbf{x}, \mathbf{x}')
  = \frac{1}{\gamma^{2}} \Jac{\transitionParams^*}{\mathbf{x}}\Jac{\transitionParams^*}{\mathbf{x}'}^\top,
\end{align}
where the kernel is the neural tangent kernel (NTK) \citep{immerImprovingPredictionsBayesian2021},
\todo{what mean function shoudl this use???}
\todo{NTK times some factor??}
with Jacobian given by $\Jac{\transitionParams}{\mathbf{x}} := \nabla_\transitionParams f(\mathbf{x})^\top \in \R^{C \times P}$
%$\mathbf{J}(\cdot) = \odv{\transitionFn(\cdot; \transitionParams)}{\transitionParams}_{\transitionParams=\transitionParams^{*}}$.
% The kernel in \cref{eq-laplace-approx-function-space} is the neural tangent kernel (NTK)
% $k(\mathbf{x}, \mathbf{x}') = \sigma_{0}^{2} J_{\transitionParams^{*}}(\mathbf{x}) J_{\transitionParams^{*}}(\mathbf{x}')^{T}$
% \citep{immerImprovingPredictionsBayesian2021}
% to formulate the GP posterior $p(f(\mathbf{X} ;\transitionParams_{0:i}) \mid \dataset_{0:i})$.
Given this GP prior, we can use \cref{eq-gp-predictive-posterior} to obtain our GP posterior by conditioning on the data.
% Given our GP prior, we can use the properties of multivariate normals to obtain our GP posterior by conditioning on the data.
% where $\mathbf{A} = \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}}$
In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
Intuitively, we can view the optimisation in \cref{eq-empirical-risk} as learning our kernel.
As a result, our NTK may be highly non stationary as it is dependent on the NN architecture, for example, the activation functions.
It is worth noting that the NTK linearises the network around the optimised parameters $\transitionParams^{*}$,
so the function space prior (and thus posterior) is only a locally linear approximation.

@@

% We start by obtaining a posterior over the weights of a trained neural network via the Laplace approximation.
% We then show how we can obtain a function-space posterior, (i.e. a GP posterior)
% by linearising the neural network around the weights Maximum a Posteriori (MAP) estimate.
% We then show that by linearising the neural network we can obtain a function-space posterior, i.e. a GP posterior.
% We paraterise our single-step dynamic model $\transitionFnWithParams : \inputDomain \rightarrow \outputDomain$
% as an $L\text{-layer}$ NN with weights $\transitionParams$.

@@

%$\mathbf{u} = f(\mathbf{Z}; \transitionParams) \in \R^{M \times C}$, known as inducing variables, where $M \ll N$.

@@

%the goal of (supervised) deep learning, is to train the weights $\transitionParams \in \R^{P}$ of an $L\text{-layer}$ NN

@@

%  \transitionParams^{*} = \arg \min_{\transitionParams \in \R^{D}} \mathcal{L}(\dataset;\transitionParams) = \arg \min_{\transitionParams \in \R^{D}} \left(
%  \sum_{n=0}^{N-1} l(f(\mathbf{x}_{n} ; \transitionParams), \mathbf{y}_{n}) + R(\transitionParams)  \right).

@@

%$l(f(\mathbf{x}_{n} ; \transitionParams),\mathbf{y}_{n}) = \|f(\mathbf{x}_{n} ; \transitionParams) - \mathbf{y}_{n} \|^{2}_{2}$
%and to use the weight decay regularizer $R(\transitionParams)=\frac{1}{2}\gamma^{-2}\|\transitionParams\|^{2}_{2}$.

@@

%  R(\transitionParams) &= \underbrace{\log p(\transitionParams)}_{\text{log prior}} = \log \mathcal{N}(\transitionParams \mid 0, \gamma^{2} \mathbf{I}) \\
%  l(f(\mathbf{x}_{n} ; \transitionParams), \mathbf{y}_{n}) &= \underbrace{\log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}; \transitionParams))}_{\text{log likelihood}}
%  = \log \mathcal{N} \left( \mathbf{y}_{n} \mid f(\mathbf{x}_{n}; \transitionParams), \mathbf{I} \right) \label{eq-log-likelihood}

@@

%function space, by linearising the BNN around $\transitionParams^{*}$ and interpretting it as a GP.

@@

%  % \transitionFn_{\transitionParams_{i}}(\cdot) \sim \mathcal{N} \left( \mu_{\transitionParams_{i}^{*}}(\cdot), K_{\transitionParams_{i}^{*}}(\cdot, \cdot') \right) \qquad
%  f(\cdot ;\transitionParams) \sim \mathcal{N} \left( \mu(\cdot), k(\cdot, \cdot') \right) \quad
%  % \mu_{\transitionParams_{i}^{*}}(\cdot)

@@

%  % = f(\cdot ;\transitionParams^{*}) \quad
%  % K_{\transitionParams_{i}^{*}}(\cdot, \cdot')

@@

%with Jacobian given by $\mathbf{J}(\cdot) = \odv{\transitionFn(\cdot; \transitionParams)}{\transitionParams}_{\transitionParams=\transitionParams^{*}}$.

@@

%% $k(\mathbf{x}, \mathbf{x}') = \sigma_{0}^{2} J_{\transitionParams^{*}}(\mathbf{x}) J_{\transitionParams^{*}}(\mathbf{x}')^{T}$

@@

%% to formulate the GP posterior $p(f(\mathbf{X} ;\transitionParams_{0:i}) \mid \dataset_{0:i})$.

@@

%It is worth noting that the NTK linearises the network around the optimised parameters $\transitionParams^{*}$,

@@

%% It is worth noting that the NTK linearises the network around the optimised parameters $\transitionParams^{*}$,

@@

%% % to write GP posterior $p(f(\mathbf{X} ;\transitionParams_{0:i}) \mid \dataset_{0:i})$ as,

@@

%%   \transitionFn_{\transitionParams_{i}}(\cdot) &\sim \mathcal{N} \left( \mu_{\transitionParams_{i}^{*}}(\cdot), K_{\transitionParams_{i}^{*}}(\cdot, \cdot') \right) \quad
%%   \mu_{\transitionParams_{i}^{*}}(\cdot) &= \transitionFn_{\transitionParams^{*}_{i}}(\cdot) \quad
%%   K_{\transitionParams_{i}^{*}}(\cdot, \cdot') &= \mathbf{J}_{\transitionParams^{*}_{i}}(\cdot) \bm\Sigma_{\transitionParams^{*}_{i}} \mathbf{J}_{\transitionParams^{*}_{i}}(\cdot')^{T}

@@

%% where the Jacobian is given by $\mathbf{J}_{\transitionParams^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\transitionParams}_{\transitionParams=\transitionParams_{i}^{*}}$.

@@

%% \mathbf{J}_{\transitionParams^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\transitionParams}_{\transitionParams=\transitionParams_{i}^{*}}

@@

%%   \transitionFn_{\transitionParams_{i}^{*}}(\cdot) &\sim \mathcal{N} \left( \mu_{\transitionParams_{i}^{*}}(\cdot), K_{\transitionParams_{i}^{*}}(\cdot, \cdot') \right) \quad
%%   \mu_{\transitionParams_{i}^{*}}(\cdot) &= \transitionFn_{\transitionParams^{*}_{i}}(\cdot) \quad
%%   K_{\transitionParams_{i}^{*}}(\cdot, \cdot') &= \mathbf{J}_{\transitionParams^{*}_{i}}(\cdot) \bm\Sigma_{\transitionParams^{*}_{i}} \mathbf{J}_{\transitionParams^{*}_{i}}(\cdot')^{T}

@@

\textbf{Laplace approximation}
The Laplace approximation \todo{add citation of original paper} constructs a Gaussian approximation of the weight-space posterior $p(\transitionParams \mid \dataset)$
by using a second-order Taylor expansion of $\mathcal{L}$ around $\transitionParams^{*}$.
The posterior approximation is given by,
\begin{align} \label{eq-laplace-approx-weight-space}
  p(\transitionParams \mid \dataset) \approx \mathcal{N} \left( \transitionParams \mid \transitionParams^{*} , \bm\Sigma_{\transitionParams^{*}} \right)
  \quad \text{with} \quad \bm\Sigma_{\transitionParams} =
 - \nabla_{\transitionParams \transitionParams}^{2} \mathcal{L} ( \dataset ; \transitionParams)|_{\transitionParams=\transitionParams^{*}}
\end{align}
That is, it sets the posterior precision to the Hessian of the loss at the optimal parameters $\transitionParams^{*}$.
It is worth noting that computing the Hessian of the loss can be computationally intractable for large networks.
The prior terms are usually trivial, so we focus on the likelihood here.
The Jacobian and Hessian of the log likelihood can be expressed per data point,
\begin{align} \label{eq-jac}
  \nabla_{\transitionParams} \log p(\mathbf{y} \mid \mathbf{f}(\mathbf{x}; \transitionParams)) &= \mathbf{J}(\mathbf{x})^{T} \mathbf{r}(\mathbf{y} ; \mathbf{f}) \\
  \nabla^{2}_{\transitionParams\transitionParams} \log p(\mathbf{y} \mid \mathbf{f}(\mathbf{x}; \transitionParams)) &= \mathbf{H}(\mathbf{x})^{T}
  \mathbf{r}(\mathbf{y};\mathbf{f}) - \mathbf{J}(\mathbf{x})^{T} \bm\Lambda(\mathbf{y};\mathbf{f}) \mathbf{J}(\mathbf{x}),
\label{eq-hess}
\end{align}
through the Jacobian $\mathbf{J} \in \R^{C \times P}$ and Hessian $\mathbf{H} \in \R^{C \times P \times P}$ of the feature extractor $\mathbf{f}(\mathbf{x}; \bm\transitionParams)$,
\begin{align} \label{eq-jac}
[\mathbf{J}(\cdot)]_{ci} = \odv{f_{c}(\cdot ; \transitionParams)}{\transitionParams_{i}}_{\transitionParams=\transitionParams^{*}} \qquad
[\mathbf{H}(\cdot)]_{cij} = \odv{f_{c}(\cdot ; \transitionParams)}{\transitionParams_{i}\transitionParams_{j}}_{\transitionParams=\transitionParams^{*}}
\end{align}
where
$\mathbf{r}(\mathbf{y}; \mathbf{f}) = \nabla_{\mathbf{f}} \log p(\mathbf{y} \mid \mathbf{f})$ can be interpreted as a residual and
$\bm\Lambda(\mathbf{y} ; \mathbf{f}) = \nabla^{2}_{\mathbf{f} \mathbf{f}} \log p(\mathbf{y} \mid \mathbf{f})$
as per-input noise.
Many approximations exist and can be used alongsied our method.
We refer the reader to \cite{daxbergerLaplace2021} for more details.
See \cref{sec-laplace-approximation} for further details on the Laplace approximation.

>>>>

% Parameters
% \newcommand{\weights}{\ensuremath{\bm\phi}}
\newcommand{\weights}{\ensuremath{\mathbf{w}}}
\newcommand{\valueFnParams}{\ensuremath{\psi}}
\newcommand{\policyParams}{\ensuremath{\theta}}

% Networks
\newcommand{\transitionFnWithParams}{\ensuremath{\transitionFn_{\weights}}}
\newcommand{\valueFn}{\ensuremath{\mathbf{Q}}}
\newcommand{\stateValueFn}{\ensuremath{\mathbf{V}}}
% \newcommand{\valueFn}{\ensuremath{\mathbf{Q}_{\valueFnParams}}}
\newcommand{\policy}{\ensuremath{\pi}}
\newcommand{\pPolicy}{\ensuremath{\pi_{\policyParams}}}

@@

\textbf{Neural Network} In supervised learning, given a data set $\dataset = \{(\mathbf{x}_{i} , \mathbf{y}_{i})\}_{i=1}^{n}$, with $\mathbf{x}_i \in \inputDomain$ and $\mathbf{y}_i \in \outputDomain$, the weights $\weights \in \R^{P}$ of a neural network
, $f_\mathbf{w} : \inputDomain \mapsto \outputDomain$, 
are usually trained to minimize the (regularized) empirical risk,
\begin{align} \label{eq-empirical-risk}
  \weights^{*} = 
  \argmin_{\weights} \mathcal{L}(\dataset,\weights) =
  \argmin_{\weights} \sum_{i=1}^{n} \ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) + \delta \mathcal{R}(\weights).
\end{align}
If $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) = -\log(p(\mathbf{y} \mid f_\weights(\mathbf{x}_{i}))$ and $\mathcal{R}(\weights) = \|\weights\|^{2}_2$ then we can view \cref{eq-empirical-risk} as the MAP solution to a Bayesian objective, where $p(\vw) = \Norm(\vzeros, \delta^{-1} \MI)$.

@@

Given this interpretation, we can represent the weight space prior from \cref{eq-log-prior}, in
function space, by linearising the BNN around $\weights^{*}$ and interpretting it as a GP.
The GP prior is then given by,
\begin{align} \label{eq-laplace-approx-function-space}
  % \transitionFn_{\weights_{i}}(\cdot) \sim \mathcal{N} \left( \mu_{\weights_{i}^{*}}(\cdot), K_{\weights_{i}^{*}}(\cdot, \cdot') \right) \qquad
  g(\vx_i) \sim \mathcal{N} \left( \mu(\vx_i), k(\vx_i, \vx_i) \right) 
  % \mu_{\weights_{i}^{*}}(\cdot)
  \mu(\cdot)
  = 0 \quad
  % = f(\cdot ;\weights^{*}) \quad
  % K_{\weights_{i}^{*}}(\cdot, \cdot')
  k(\mathbf{x}, \mathbf{x}')
  = \frac{1}{\gamma^{2}} \Jac{\weights^*}{\mathbf{x}}\Jac{\weights^*}{\mathbf{x}'}^\top,
\end{align}
where the kernel is the neural tangent kernel (NTK) \citep{immerImprovingPredictionsBayesian2021},
\todo{what mean function shoudl this use???}
\todo{NTK times some factor??}
with Jacobian given by $\Jac{\weights}{\mathbf{x}} := \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$
%$\mathbf{J}(\cdot) = \odv{\transitionFn(\cdot; \weights)}{\weights}_{\weights=\weights^{*}}$.
% The kernel in \cref{eq-laplace-approx-function-space} is the neural tangent kernel (NTK)
% $k(\mathbf{x}, \mathbf{x}') = \sigma_{0}^{2} J_{\weights^{*}}(\mathbf{x}) J_{\weights^{*}}(\mathbf{x}')^{T}$
% \citep{immerImprovingPredictionsBayesian2021}
% to formulate the GP posterior $p(f(\mathbf{X} ;\weights_{0:i}) \mid \dataset_{0:i})$.
Given this GP prior, we can use \cref{eq-gp-predictive-posterior} to obtain our GP posterior by conditioning on the data.
% Given our GP prior, we can use the properties of multivariate normals to obtain our GP posterior by conditioning on the data.
% where $\mathbf{A} = \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}}$
In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
Intuitively, we can view the optimisation in \cref{eq-empirical-risk} as learning our kernel.
As a result, our NTK may be highly non stationary as it is dependent on the NN architecture, for example, the activation functions.
It is worth noting that the NTK linearises the network around the optimised parameters $\weights^{*}$,
so the function space prior (and thus posterior) is only a locally linear approximation.

@@

% We start by obtaining a posterior over the weights of a trained neural network via the Laplace approximation.
% We then show how we can obtain a function-space posterior, (i.e. a GP posterior)
% by linearising the neural network around the weights Maximum a Posteriori (MAP) estimate.
% We then show that by linearising the neural network we can obtain a function-space posterior, i.e. a GP posterior.
% We paraterise our single-step dynamic model $\transitionFnWithParams : \inputDomain \rightarrow \outputDomain$
% as an $L\text{-layer}$ NN with weights $\weights$.

@@

%$\mathbf{u} = f(\mathbf{Z}; \weights) \in \R^{M \times C}$, known as inducing variables, where $M \ll N$.

@@

%the goal of (supervised) deep learning, is to train the weights $\weights \in \R^{P}$ of an $L\text{-layer}$ NN

@@

%  \weights^{*} = \arg \min_{\weights \in \R^{D}} \mathcal{L}(\dataset;\weights) = \arg \min_{\weights \in \R^{D}} \left(
%  \sum_{n=0}^{N-1} l(f(\mathbf{x}_{n} ; \weights), \mathbf{y}_{n}) + R(\weights)  \right).

@@

%$l(f(\mathbf{x}_{n} ; \weights),\mathbf{y}_{n}) = \|f(\mathbf{x}_{n} ; \weights) - \mathbf{y}_{n} \|^{2}_{2}$
%and to use the weight decay regularizer $R(\weights)=\frac{1}{2}\gamma^{-2}\|\weights\|^{2}_{2}$.

@@

%  R(\weights) &= \underbrace{\log p(\weights)}_{\text{log prior}} = \log \mathcal{N}(\weights \mid 0, \gamma^{2} \mathbf{I}) \\
%  l(f(\mathbf{x}_{n} ; \weights), \mathbf{y}_{n}) &= \underbrace{\log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}; \weights))}_{\text{log likelihood}}
%  = \log \mathcal{N} \left( \mathbf{y}_{n} \mid f(\mathbf{x}_{n}; \weights), \mathbf{I} \right) \label{eq-log-likelihood}

@@

%function space, by linearising the BNN around $\weights^{*}$ and interpretting it as a GP.

@@

%  % \transitionFn_{\weights_{i}}(\cdot) \sim \mathcal{N} \left( \mu_{\weights_{i}^{*}}(\cdot), K_{\weights_{i}^{*}}(\cdot, \cdot') \right) \qquad
%  f(\cdot ;\weights) \sim \mathcal{N} \left( \mu(\cdot), k(\cdot, \cdot') \right) \quad
%  % \mu_{\weights_{i}^{*}}(\cdot)

@@

%  % = f(\cdot ;\weights^{*}) \quad
%  % K_{\weights_{i}^{*}}(\cdot, \cdot')

@@

%with Jacobian given by $\mathbf{J}(\cdot) = \odv{\transitionFn(\cdot; \weights)}{\weights}_{\weights=\weights^{*}}$.

@@

%% $k(\mathbf{x}, \mathbf{x}') = \sigma_{0}^{2} J_{\weights^{*}}(\mathbf{x}) J_{\weights^{*}}(\mathbf{x}')^{T}$

@@

%% to formulate the GP posterior $p(f(\mathbf{X} ;\weights_{0:i}) \mid \dataset_{0:i})$.

@@

%It is worth noting that the NTK linearises the network around the optimised parameters $\weights^{*}$,

@@

%% It is worth noting that the NTK linearises the network around the optimised parameters $\weights^{*}$,

@@

%% % to write GP posterior $p(f(\mathbf{X} ;\weights_{0:i}) \mid \dataset_{0:i})$ as,

@@

%%   \transitionFn_{\weights_{i}}(\cdot) &\sim \mathcal{N} \left( \mu_{\weights_{i}^{*}}(\cdot), K_{\weights_{i}^{*}}(\cdot, \cdot') \right) \quad
%%   \mu_{\weights_{i}^{*}}(\cdot) &= \transitionFn_{\weights^{*}_{i}}(\cdot) \quad
%%   K_{\weights_{i}^{*}}(\cdot, \cdot') &= \mathbf{J}_{\weights^{*}_{i}}(\cdot) \bm\Sigma_{\weights^{*}_{i}} \mathbf{J}_{\weights^{*}_{i}}(\cdot')^{T}

@@

%% where the Jacobian is given by $\mathbf{J}_{\weights^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\weights}_{\weights=\weights_{i}^{*}}$.

@@

%% \mathbf{J}_{\weights^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\weights}_{\weights=\weights_{i}^{*}}

@@

%%   \transitionFn_{\weights_{i}^{*}}(\cdot) &\sim \mathcal{N} \left( \mu_{\weights_{i}^{*}}(\cdot), K_{\weights_{i}^{*}}(\cdot, \cdot') \right) \quad
%%   \mu_{\weights_{i}^{*}}(\cdot) &= \transitionFn_{\weights^{*}_{i}}(\cdot) \quad
%%   K_{\weights_{i}^{*}}(\cdot, \cdot') &= \mathbf{J}_{\weights^{*}_{i}}(\cdot) \bm\Sigma_{\weights^{*}_{i}} \mathbf{J}_{\weights^{*}_{i}}(\cdot')^{T}

@@

\textbf{Laplace approximation}
The Laplace approximation \todo{add citation of original paper} constructs a Gaussian approximation of the weight-space posterior $p(\weights \mid \dataset)$
by using a second-order Taylor expansion of $\mathcal{L}$ around $\weights^{*}$.
The posterior approximation is given by,
\begin{align} \label{eq-laplace-approx-weight-space}
  p(\weights \mid \dataset) \approx \mathcal{N} \left( \weights \mid \weights^{*} , \bm\Sigma_{\weights^{*}} \right)
  \quad \text{with} \quad \bm\Sigma_{\weights} =
 - \nabla_{\weights \weights}^{2} \mathcal{L} ( \dataset ; \weights)|_{\weights=\weights^{*}}
\end{align}
That is, it sets the posterior precision to the Hessian of the loss at the optimal parameters $\weights^{*}$.
It is worth noting that computing the Hessian of the loss can be computationally intractable for large networks.
The prior terms are usually trivial, so we focus on the likelihood here.
The Jacobian and Hessian of the log likelihood can be expressed per data point,
\begin{align} \label{eq-jac}
  \nabla_{\weights} \log p(\mathbf{y} \mid \mathbf{f}(\mathbf{x}; \weights)) &= \mathbf{J}(\mathbf{x})^{T} \mathbf{r}(\mathbf{y} ; \mathbf{f}) \\
  \nabla^{2}_{\weights\weights} \log p(\mathbf{y} \mid \mathbf{f}(\mathbf{x}; \weights)) &= \mathbf{H}(\mathbf{x})^{T}
  \mathbf{r}(\mathbf{y};\mathbf{f}) - \mathbf{J}(\mathbf{x})^{T} \bm\Lambda(\mathbf{y};\mathbf{f}) \mathbf{J}(\mathbf{x}),
\label{eq-hess}
\end{align}
through the Jacobian $\mathbf{J} \in \R^{C \times P}$ and Hessian $\mathbf{H} \in \R^{C \times P \times P}$ of the feature extractor $\mathbf{f}(\mathbf{x}; \bm\weights)$,
\begin{align} \label{eq-jac}
[\mathbf{J}(\cdot)]_{ci} = \odv{f_{c}(\cdot ; \weights)}{\weights_{i}}_{\weights=\weights^{*}} \qquad
[\mathbf{H}(\cdot)]_{cij} = \odv{f_{c}(\cdot ; \weights)}{\weights_{i}\weights_{j}}_{\weights=\weights^{*}}
\end{align}
where
$\mathbf{r}(\mathbf{y}; \mathbf{f}) = \nabla_{\mathbf{f}} \log p(\mathbf{y} \mid \mathbf{f})$ can be interpreted as a residual and
$\bm\Lambda(\mathbf{y} ; \mathbf{f}) = \nabla^{2}_{\mathbf{f} \mathbf{f}} \log p(\mathbf{y} \mid \mathbf{f})$
as per-input noise.
Many approximations exist and can be used alongsied our method.
We refer the reader to \cite{daxbergerLaplace2021} for more details.
See \cref{sec-laplace-approximation} for further details on the Laplace approximation.
